Interpretable Machine Learning for Science \\ with PySR and SymbolicRegression.jl

### 2023-05-04 src/tex/ms.tex
Fix incorrect expression variable in algorithm

\begin{algorithm}[h!]
\algsize
\DontPrintSemicolon
\Data{$E$, an expression}
\Data{$T$, the annealing temperature $\in [0, 1]$}
\Result{mutated version of $E$}
\Param{$m_i$, for $i=1,\ldots,8$, the probability weight of mutation type $i$}
\Param{$f$, the constant perturbation scale (=1)}
\Param{$\epsilon$, the minimum perturbation (=0.1)}
\Param{$\alpha$, the temperature scale (=0.1)}
\BlankLine
\Fn{\Mutate{$E, T$} \algcomment{\href{https://github.com/MilesCranmer/SymbolicRegression.jl/blob/0bb8b2bb58a4338729c84e3f52575ac475c86a09/src/Mutate.jl\#L22-L261}{[code]}}}{
adjust weights $w_1, \ldots, w_8$ based on constraints\;
$i \gets$ random choice of $ 1, \ldots, 8$ weighted by $w_1, \ldots, w_8$\;
\SetKwRepeat{Do}{do}{until}
\Do{\textnormal{\SatisfiesConstraints{$E^\ast$}}}{
    $E^\ast \gets $ \Copy{$E$}\;
    \Switch{$i$}{
        \Case(\algcomment{mutate constant}){$1$}{
            $a \gets  (1 + f \times T + \epsilon)^{2\times \Rand{} - 1}$\;
            \If{\Rand{} $< 0.5$}{
                $a \gets -a$
            }
            multiply random constant in $E$ by $a$
        }
        \Case(\algcomment{mutate operator}){$2$}{
            randomly replace an operator in $E$ with\\
            \ \ an operator of the same degree
        }
        \Case(\algcomment{append/prepend node}){$3$}{
            add random node to root or leaf of $E$
        }
        \Case(\algcomment{insert node}){$4$}{
            insert a random node inside $E$
        }
        \Case(\algcomment{delete subtree}){$5$}{
            replace a node and its children from $E$\\
            \ \ with a constant or variable
        }
        \Case(\algcomment{simplify tree}){$6$}{
            simplify $E$
        }
        \Case(\algcomment{new tree entirely}){$7$}{
            $E \gets $ random expression
        }
        \Case(\algcomment{no mutation}){$8$}{
            do nothing
        }
    }
}
\BlankLine
$C, C^\ast \gets$ complexity of expressions $E, E^\ast$, respectively\;
$L, L^\ast \gets$ accuracy of expressions $E, E^\ast$, respectively\;
$q_\text{anneal} \gets \exp(-\frac{L^\ast - L}{\alpha \times T})$\;
$C \gets$ complexity of expressions $E$\;
$q_\text{parsimony} \gets \frac{ \text{frecency}[C] }{ \text{frecency}[C]}$\;
\eIf{\Rand{} $< q_\text{anneal} \cdot q_\text{parsimony}$}{
    \KwRet{$E^\ast$}
}{
    \KwRet{$E$}
}
}
\caption{Mutations.\label{alg:mutate} }
\end{algorithm}

>>>>

\begin{algorithm}[h!]
\algsize
\DontPrintSemicolon
\Data{$E$, an expression}
\Data{$T$, the annealing temperature $\in [0, 1]$}
\Result{mutated version of $E$}
\Param{$m_i$, for $i=1,\ldots,8$, the probability weight of mutation type $i$}
\Param{$f$, the constant perturbation scale (=1)}
\Param{$\epsilon$, the minimum perturbation (=0.1)}
\Param{$\alpha$, the temperature scale (=0.1)}
\BlankLine
\Fn{\Mutate{$E, T$} \algcomment{\href{https://github.com/MilesCranmer/SymbolicRegression.jl/blob/0bb8b2bb58a4338729c84e3f52575ac475c86a09/src/Mutate.jl\#L22-L261}{[code]}}}{
adjust weights $w_1, \ldots, w_8$ based on constraints\;
$i \gets$ random choice of $ 1, \ldots, 8$ weighted by $w_1, \ldots, w_8$\;
\SetKwRepeat{Do}{do}{until}
\Do{\textnormal{\SatisfiesConstraints{$E^\ast$}}}{
    $E^\ast \gets $ \Copy{$E$}\;
    \Switch{$i$}{
        \Case(\algcomment{mutate constant}){$1$}{
            $a \gets  (1 + f \times T + \epsilon)^{2\times \Rand{} - 1}$\;
            \If{\Rand{} $< 0.5$}{
                $a \gets -a$
            }
            multiply random constant in $E^\ast$ by $a$
        }
        \Case(\algcomment{mutate operator}){$2$}{
            randomly replace an operator in $E^\ast$ with\\
            \ \ an operator of the same degree
        }
        \Case(\algcomment{append/prepend node}){$3$}{
            add random node to root or leaf of $E^\ast$
        }
        \Case(\algcomment{insert node}){$4$}{
            insert a random node inside $E^\ast$
        }
        \Case(\algcomment{delete subtree}){$5$}{
            replace a node and its children from $E^\ast$\\
            \ \ with a constant or variable
        }
        \Case(\algcomment{simplify tree}){$6$}{
            simplify $E^\ast$
        }
        \Case(\algcomment{new tree entirely}){$7$}{
            $E^\ast \gets $ random expression
        }
        \Case(\algcomment{no mutation}){$8$}{
            do nothing
        }
    }
}
\BlankLine
$C, C^\ast \gets$ complexity of expressions $E, E^\ast$, respectively\;
$L, L^\ast \gets$ accuracy of expressions $E, E^\ast$, respectively\;
$q_\text{anneal} \gets \exp(-\frac{L^\ast - L}{\alpha \times T})$\;
$C \gets$ complexity of expressions $E$\;
$q_\text{parsimony} \gets \frac{ \text{frecency}[C] }{ \text{frecency}[C]}$\;
\eIf{\Rand{} $< q_\text{anneal} \cdot q_\text{parsimony}$}{
    \KwRet{$E^\ast$}
}{
    \KwRet{$E$}
}
}
\caption{Mutations.\label{alg:mutate} }
\end{algorithm}
